The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-23 crelle-dictionary.tex
moved the current file back to the main directory
Current file: crelle-dictionary.tex.
Bibliography style is not correct.

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%

\begin{thebibliography}{9}

\bibitem{article}
\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.

\bibitem{preprint}
\textit{C.~Bonnaf\'e},
Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.

\bibitem{proceedings}
\textit{P. Brooksbank},
Article in a conference proceedings,
in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.

\bibitem{phdthesis}
\textit{J.~D.~King},
Unpublished dissertation,
Ph.D. thesis, University of Cambridge, 1995.

\bibitem{book}
\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
Book, 2nd ed., De Gruyter, Berlin 2012.

\end{thebibliography}

\bibliographystyle{amsalpha}
\bibliography{bibliography/Biblio}

@@

\begin{table}[ht]
\caption{A big diagram}
\begin{center}
{\smaller\smaller\smaller
    \[
  \begin{tikzcd}[row sep=20, column sep=3]
&   &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
& &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
&   {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
& && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
0  \arrow{rr} & & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
    \arrow{rr}  &   & 0 & \\
& \Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
0  \arrow{rr} & & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
    \arrow{rr}&& 0 & \\
& %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
 && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
 \\
& & 0  && 0  &&  0  && & \\
 &      &&  0 && 0 && 0 & & \\
  \end{tikzcd}
  \]
}
\end{center}
\label{diagram}
\end{table}

%sagemathcloud={"zoom_width":105}

>>>>

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%
%\bibliographystyle{amsalpha}
\bibliography{bibliography/Biblio}

@@
